caDDS: Community Assisted Distributed Database for Sequences

### 2020-06-19 Paper2020ACM/Presentation.tex
Edited presentation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% INTRO + RRL %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Abstract}
\end{frame}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% INTRO + RRL %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Abstract}
  Genomic data the past few years have grown exponentially with the technology barely keeping up. The problem faced by genome researchers is the large data set and difficulty transferring the files. Previous distributed databases are either not meant for genomic data, or difficult to replicate. This paper lays the groundwork for a distributed database that is designed to easily scale to accommodate bigger storage, and also reduces the data speed bottleneck faced by centralized databases. The proposed system has a master node and data nodes. Data nodes should theoretically increase data transfer speeds even as the number of users increase. (to be updated based on conclusion) While current databases(e.g. NCBI) have more data, more users, and a live platform. The proposed system is aimed towards a smaller community, with more frequent and localized data, which the data storage can easily be expanded as the need arises. A recommendation is to implement the system and make the code public for the use of other communities.
\end{frame}
